Delving into the World Inside Prisons for Safety, Health, and Isolation

### 2024-02-11 outputs/paper/paper.qmd
change

@@

```{r fig.height=10, fig.width=10}
#| label: Bills of penguins
#| fig-cap: Cumulative COVID-19 Case Rates among Those in Prison Staff and General Population
#| echo: false

@@

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

@@

## Diagnostics

>>>>

\ In addition to replicating the original data, we have incorporated a comparison of the COVID-19 infection rate among prison staff with the overall U.S. COVID-19 infection rate. According to the figure(@fig-staff), the infection rate among prison staff surpasses the overall infection rate but remains lower than the new coronavirus infection rate among incarcerated individuals, positioning it roughly in the middle between the two. This observation underscores the vulnerable position of prisoners within correctional facilities during the pandemic.

## Weaknesses
### Bias in Data Analysis
On one hand, it's noteworthy that a considerable portion of data regarding U.S. prisons exclusively pertains to men, leading to the phenomenon referred to as "big dick data." This term underscores the prevalence of male-dominated datasets, which not only underscores systemic bias and marginalization, particularly towards women but also sheds light on existing power dynamics. The absence or marginalization of women in these datasets not only mirrors prevailing power structures but also perpetuates gender-based biases and stereotypes. Such gender disparity distorts our comprehension of reality, reinforces harmful stereotypes and inequalities, and presents substantial hurdles to data-driven decision-making (@dignazio2020data).

\ On the other hand, when examining racial data, it tends to be categorized broadly into whites and blacks. This practice not only reinforces the binary opposition between these two racial groups in the United States but also overlooks the experiences of other ethnic minorities.

### Measurement error
Utilizing data from various origins, a practice known as data fusion or integration, introduces complexities and hurdles that can result in measurement inaccuracies. Each dataset carries its unique biases, constraints, and inaccuracies stemming from variations in data collection methods, sampling approaches, measurement tools, and processing methodologies.

The amalgamation of data from disparate sources often introduces disparities in quality, consistency, and reliability, leading to inconsistencies or inaccuracies in the merged datasets. Moreover, issues like incomplete data, absent values, and misclassification errors can compound measurement inaccuracies.

## future
On the one hand, similar data collection, statistical analysis, and comparative studies of Canadian prisons provide an attractive avenue for gaining insights due to Canada's geographic proximity to the United States and some shared cultural and legal frameworks. This similarity in land area and certain social aspects may allow for more meaningful comparisons and broader conclusions.

On the other hand, a comparison of prison data from smaller Nordic countries, represented by Iceland, gives a markedly different context. These countries tend to have very different social norms, legal frameworks, and approaches to criminal justice than North American countries. Factors such as smaller population sizes, different cultural attitudes toward crime and punishment, and alternative approaches to rehabilitation may contribute to contrasting prison data.

Apart from large-scale studies, conducting small controlled experiments could offer valuable insights into the influence of different prison environments on the physical and mental well-being of inmates.

Studying the experiences of prison staff can provide insight into challenges within correctional facilities and facilitate the development of effective policies. Likewise, exploring the impact of incarceration on families can provide greater insight into broader social impacts, including emotional distress and financial stress. Including their voices in research and policy discussions is critical to addressing the complex issues surrounding incarceration and reentry.

@@

```{r fig.height=10, fig.width=10}
#| label: fig-staff
#| fig-cap: Cumulative COVID-19 Case Rates among Those in Prison Staff and General Population
#| echo: false

@@

@@
